---
title: "GeoCoding_FourIncident"
output: html_document
---
```{r}
# Calling package dplyr
library(dplyr)
# Don't delete this chunk if you are using the DataComputing package
library(mosaic)
library(ggmap)
library(lubridate)
```

```{r}
infile <- "datav16810"
data <- read.csv(paste0('./', infile, '.csv'))
# get the address list, and append "Cincinnati" to the end to increase accuracy 
# (change or remove this if your address already include a country etc.)
addresses = data$ADDRESS_X
addresses = paste0(addresses, ", Cincinnati")
```

```{r}
for(i in 16810:nrow(data))
{
  if (is.na(data$LATITUDE_X[i])){
  print(paste("Working on index", i, "of", nrow(data)))
  result <- geocode(addresses[i], output = "latlona", source = "google")
  data$LONGITUDE_X[i] <- as.numeric(result[1])
  data$LATITUDE_X[i] <- as.numeric(result[2])
  }
}

```

```{r}
write.csv(data, file = "data.csv")
getwd() #get working directory-> find the data.csv file in this folder and upload it to github
```

```{r}
#combine the v2 dataset into main dataset, data is 16810
for(i in 19727:22296)
{
  data$LONGITUDE_X[i] <- as.numeric(datav2v22647$LONGITUDE_X[i])
  data$LATITUDE_X[i] <- as.numeric(datav2v22647$LATITUDE_X[i])
}
```
```{r}
#combine the v3 dataset into main dataset, data is 16810
for(i in 22296:24959)
{
  data$LONGITUDE_X[i] <- as.numeric(datav3v25182$LONGITUDE_X[i])
  data$LATITUDE_X[i] <- as.numeric(datav3v25182$LATITUDE_X[i])
}
```
```{r}
#combine the v4 dataset into main dataset, data is 16810
for(i in 24959:27489)
{
  data$LONGITUDE_X[i] <- as.numeric(datav4v27843$LONGITUDE_X[i])
  data$LATITUDE_X[i] <- as.numeric(datav4v27843$LATITUDE_X[i])
}
```
```{r}
#combine the v5 dataset into main dataset, data is 16810
for(i in 27489:59274)
{
  data$LONGITUDE_X[i] <- as.numeric(datav5v59274$LONGITUDE_X[i])
  data$LATITUDE_X[i] <- as.numeric(datav5v59274$LATITUDE_X[i])
}
```
```{r}
#combine the v1 dataset into main dataset, data is 16810
for(i in 16810:19727)
{
  data$LONGITUDE_X[i] <- as.numeric(datav1$LONGITUDE_X[i])
  data$LATITUDE_X[i] <- as.numeric(datav1$LATITUDE_X[i])
}
```

```{r}
write.csv(data, file = "data_fourtype_wNA.csv")
```

```{r}
fourtype_nNA <- data %>%
  filter(!is.na(LATITUDE_X) & !is.na(LONGITUDE_X))
```

```{r}
fourtype_ymd<-
  fourtype_nNA %>%
  select(X, ADDRESS_X,LATITUDE_X,LONGITUDE_X,CREATE_TIME_INCIDENT,INCIDENT_TYPE_DESC,NEIGHBORHOOD,STREET_SRCH,ARRIVAL_TIME_PRIMARY_UNIT,CLOSED_TIME_INCIDENT,DISPATCH_TIME_PRIMARY_UNIT) %>%
  mutate(date=
           lubridate::mdy_hms(CREATE_TIME_INCIDENT))%>%
  mutate(year=
           lubridate::year(date))%>%
  mutate(month=
           lubridate::month(date))%>%
  mutate(day=
           lubridate::day(date)) 
View(fourtype_ymd)
```

```{r}
write.csv(fourtype_ymd, file = "fourtype_ymd.csv")
```
summary(fourtype_ymd)
       X                         ADDRESS_X       LATITUDE_X      LONGITUDE_X     
 Min.   :    1   23XX FERGUSON RD     :  341   Min.   :-25.29   Min.   :-122.10  
 1st Qu.:17146   61XX GLENWAY AV      :  283   1st Qu.: 39.11   1st Qu.: -84.56  
 Median :35506   60XX GLENWAY AV      :  205   Median : 39.14   Median : -84.52  
 Mean   :32692   34XX SPRING GROVE AV :  190   Mean   : 39.11   Mean   : -84.49  
 3rd Qu.:47385   36XX WARSAW AV       :  160   3rd Qu.: 39.16   3rd Qu.: -84.48  
 Max.   :59274   3XX EZZARD CHARLES DR:  149   Max.   : 47.71   Max.   :  79.83  
                 (Other)              :45732                                     
             CREATE_TIME_INCIDENT    INCIDENT_TYPE_DESC          NEIGHBORHOOD  
 01/15/2016 08:49:14 PM:    2     bulglar     : 6603    WESTWOOD       : 4159  
 01/15/2017 09:30:40 PM:    2     car_accident:17300    N/A            : 3646  
 02/26/2016 05:23:30 PM:    2     shooting    : 4717    EAST PRICE HILL: 2526  
 03/11/2015 04:26:09 PM:    2     theft_pro   :18440    WEST PRICE HILL: 2156  
 03/22/2016 04:01:12 PM:    2                           OVER-THE-RHINE : 2135  
 04/25/2016 06:46:06 PM:    2                           AVONDALE       : 2083  
 (Other)               :47048                           (Other)        :30355  
          STREET_SRCH             ARRIVAL_TIME_PRIMARY_UNIT             CLOSED_TIME_INCIDENT
 GLENWAY AV     : 1269   02/20/2015 04:49:50 PM:    2       02/24/2015 04:22:52 PM:    2    
 READING RD     : 1094   02/24/2015 08:15:51 AM:    2       03/19/2015 07:35:45 AM:    2    
 VINE ST        : 1081   03/26/2016 04:28:37 AM:    2       04/03/2015 05:55:37 PM:    2    
 MADISON RD     :  485   03/28/2015 07:58:43 PM:    2       04/18/2015 09:11:19 PM:    2    
 WARSAW AV      :  472   04/09/2015 02:29:23 PM:    2       06/02/2015 04:11:09 PM:    2    
 SPRING GROVE AV:  465   (Other)               :38033       (Other)               :46838    
 (Other)        :42194   NA's                  : 9017       NA's                  :  212    
          DISPATCH_TIME_PRIMARY_UNIT      date                          year     
 03/17/2015 12:37:55 PM:    2        Min.   :2015-01-01 00:01:45   Min.   :2015  
 03/20/2016 06:07:33 PM:    2        1st Qu.:2015-08-03 13:10:57   1st Qu.:2015  
 03/22/2016 07:00:30 PM:    2        Median :2016-03-02 15:46:24   Median :2016  
 06/02/2016 07:11:27 PM:    2        Mean   :2016-03-19 05:41:08   Mean   :2016  
 06/08/2017 12:31:37 PM:    2        3rd Qu.:2016-09-28 16:56:50   3rd Qu.:2016  
 (Other)               :42094        Max.   :2017-10-17 00:27:55   Max.   :2017  
 NA's                  : 4956                                                    
     month             day       
 Min.   : 1.000   Min.   : 1.00  
 1st Qu.: 4.000   1st Qu.: 8.00  
 Median : 7.000   Median :16.00  
 Mean   : 6.589   Mean   :15.58  
 3rd Qu.: 9.000   3rd Qu.:23.00  
 Max.   :12.000   Max.   :31.00  
                                 
```{r}
summary(fourtype_ymd$LATITUDE_X)
summary(fourtype_ymd$LONGITUDE_X)
quantile(fourtype_ymd$LATITUDE_X, c(.005, .57, .995)) 
quantile(fourtype_ymd$LONGITUDE_X, c(.025, .57, .975)) 
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  -25.29   39.11   39.14   39.11   39.16   47.71 
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# -122.10  -84.56  -84.52  -84.49  -84.48   79.83 
#     0.5%      57%    99.5% 
# 39.06249 39.14238 39.28465 
#      0.5%       57%     99.5% 
# -84.70742 -84.51188 -84.37261 
```
```{r}
fourtype_ymd_cincin<-
  fourtype_ymd %>%
  arrange(LATITUDE_X,LONGITUDE_X)%>%
  filter(LATITUDE_X > 39.088, LONGITUDE_X > -84.578) %>%
  filter(LATITUDE_X < 39.165, LONGITUDE_X < -84.469) 
  
```
```{r}
summary(fourtype_ymd_cincin$LATITUDE_X)
summary(fourtype_ymd_cincin$LONGITUDE_X)
```
```{r}
write.csv(fourtype_ymd_995, file = "fourtype_ymd_995.csv")
```

```{r}
dx = (39.28-39.06)/5 #latitude
dy = (-84.37+84.70)/30 #longitude
```

```{r}
a = c(1:6)
b = c(1:31)
for (i in c(1:6)) {
  a[i] = 39.06+(i-1)*dx
}
for (i in c(1:31)) {
  b[i] = -84.70+(i-1)*dy
}
```


```{r}
fourtype_995_reg <-
  fourtype_ymd_995 %>%
  mutate(region = derivedFactor(
      "1" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[1] < LONGITUDE_X & LONGITUDE_X<= b[2]),
     "2" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[2] < LONGITUDE_X & LONGITUDE_X <= b[3]),
     "3" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[3] < LONGITUDE_X & LONGITUDE_X<= b[4]),
     "4" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[4] < LONGITUDE_X & LONGITUDE_X <= b[5]),
     "5" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[5] < LONGITUDE_X & LONGITUDE_X<= b[6]),
     "6" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[6] < LONGITUDE_X & LONGITUDE_X <= b[7]),
     "7" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[7] < LONGITUDE_X & LONGITUDE_X<= b[8]),
     "8" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[8] < LONGITUDE_X & LONGITUDE_X <= b[9]),
     "9" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[9] < LONGITUDE_X & LONGITUDE_X<= b[10]),
     "10" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[10] < LONGITUDE_X & LONGITUDE_X <= b[11]),
      "11" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[11] < LONGITUDE_X & LONGITUDE_X<= b[12]),
     "12" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[12] < LONGITUDE_X & LONGITUDE_X <= b[13]),
     "13" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[13] < LONGITUDE_X & LONGITUDE_X<= b[14]),
     "14" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[14] < LONGITUDE_X & LONGITUDE_X <= b[15]),
     "15" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[15] < LONGITUDE_X & LONGITUDE_X<= b[16]),
     "16" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[16] < LONGITUDE_X & LONGITUDE_X <= b[17]),
     "17" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[17] < LONGITUDE_X & LONGITUDE_X<= b[18]),
     "18" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[18] < LONGITUDE_X & LONGITUDE_X <= b[19]),
     "19" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[19] < LONGITUDE_X & LONGITUDE_X<= b[20]),
     "20" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[20] < LONGITUDE_X & LONGITUDE_X <= b[21]),
      "21" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[21] < LONGITUDE_X & LONGITUDE_X<= b[22]),
     "22" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[22] < LONGITUDE_X & LONGITUDE_X <= b[23]),
     "23" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[23] < LONGITUDE_X & LONGITUDE_X<= b[24]),
     "24" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[24] < LONGITUDE_X & LONGITUDE_X <= b[25]),
     "25" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[25] < LONGITUDE_X & LONGITUDE_X<= b[26]),
     "26" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[26] < LONGITUDE_X & LONGITUDE_X <= b[27]),
     "27" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[27] < LONGITUDE_X & LONGITUDE_X<= b[28]),
     "28" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[28] < LONGITUDE_X & LONGITUDE_X <= b[29]),
     "29" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[29] < LONGITUDE_X & LONGITUDE_X<= b[30]),
     "30" = ( a[1] <= LATITUDE_X & LATITUDE_X <= a[2] & b[30] < LONGITUDE_X & LONGITUDE_X <= b[31]),
     
     
     "31" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[1] < LONGITUDE_X & LONGITUDE_X<= b[2]),
     "32" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[2] < LONGITUDE_X & LONGITUDE_X <= b[3]),
     "33" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[3] < LONGITUDE_X & LONGITUDE_X<= b[4]),
     "34" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[4] < LONGITUDE_X & LONGITUDE_X <= b[5]),
     "35" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[5] < LONGITUDE_X & LONGITUDE_X<= b[6]),
     "36" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[6] < LONGITUDE_X & LONGITUDE_X <= b[7]),
     "37" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[7] < LONGITUDE_X & LONGITUDE_X<= b[8]),
     "38" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[8] < LONGITUDE_X & LONGITUDE_X <= b[9]),
     "39" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[9] < LONGITUDE_X & LONGITUDE_X<= b[10]),
     "40" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[10] < LONGITUDE_X & LONGITUDE_X <= b[11]),
      "41" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[11] < LONGITUDE_X & LONGITUDE_X<= b[12]),
     "42" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[12] < LONGITUDE_X & LONGITUDE_X <= b[13]),
     "43" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[13] < LONGITUDE_X & LONGITUDE_X<= b[14]),
     "44" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[14] < LONGITUDE_X & LONGITUDE_X <= b[15]),
     "45" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[15] < LONGITUDE_X & LONGITUDE_X<= b[16]),
     "46" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[16] < LONGITUDE_X & LONGITUDE_X <= b[17]),
     "47" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[17] < LONGITUDE_X & LONGITUDE_X<= b[18]),
     "48" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[18] < LONGITUDE_X & LONGITUDE_X <= b[19]),
     "49" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[19] < LONGITUDE_X & LONGITUDE_X<= b[20]),
     "50" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[20] < LONGITUDE_X & LONGITUDE_X <= b[21]),
      "51" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[21] < LONGITUDE_X & LONGITUDE_X<= b[22]),
     "52" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[22] < LONGITUDE_X & LONGITUDE_X <= b[23]),
     "53" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[23] < LONGITUDE_X & LONGITUDE_X<= b[24]),
     "54" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[24] < LONGITUDE_X & LONGITUDE_X <= b[25]),
     "55" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[25] < LONGITUDE_X & LONGITUDE_X<= b[26]),
     "56" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[26] < LONGITUDE_X & LONGITUDE_X <= b[27]),
     "57" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[27] < LONGITUDE_X & LONGITUDE_X<= b[28]),
     "58" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[28] < LONGITUDE_X & LONGITUDE_X <= b[29]),
     "59" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[29] < LONGITUDE_X & LONGITUDE_X<= b[30]),
     "60" = ( a[2] <= LATITUDE_X & LATITUDE_X <= a[3] & b[30] < LONGITUDE_X & LONGITUDE_X <= b[31]),
     
     
     
     "61" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[1] < LONGITUDE_X & LONGITUDE_X<= b[2]),
     "62" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[2] < LONGITUDE_X & LONGITUDE_X <= b[3]),
     "63" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[3] < LONGITUDE_X & LONGITUDE_X<= b[4]),
     "64" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[4] < LONGITUDE_X & LONGITUDE_X <= b[5]),
     "65" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[5] < LONGITUDE_X & LONGITUDE_X<= b[6]),
     "66" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[6] < LONGITUDE_X & LONGITUDE_X <= b[7]),
     "67" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[7] < LONGITUDE_X & LONGITUDE_X<= b[8]),
     "68" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[8] < LONGITUDE_X & LONGITUDE_X <= b[9]),
     "69" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[9] < LONGITUDE_X & LONGITUDE_X<= b[10]),
     "70" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[10] < LONGITUDE_X & LONGITUDE_X <= b[11]),
      "71" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[11] < LONGITUDE_X & LONGITUDE_X<= b[12]),
     "72" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[12] < LONGITUDE_X & LONGITUDE_X <= b[13]),
     "73" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[13] < LONGITUDE_X & LONGITUDE_X<= b[14]),
     "74" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[14] < LONGITUDE_X & LONGITUDE_X <= b[15]),
     "75" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[15] < LONGITUDE_X & LONGITUDE_X<= b[16]),
     "76" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[16] < LONGITUDE_X & LONGITUDE_X <= b[17]),
     "77" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[17] < LONGITUDE_X & LONGITUDE_X<= b[18]),
     "78" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[18] < LONGITUDE_X & LONGITUDE_X <= b[19]),
     "79" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[19] < LONGITUDE_X & LONGITUDE_X<= b[20]),
     "80" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[20] < LONGITUDE_X & LONGITUDE_X <= b[21]),
      "81" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[21] < LONGITUDE_X & LONGITUDE_X<= b[22]),
     "82" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[22] < LONGITUDE_X & LONGITUDE_X <= b[23]),
     "83" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[23] < LONGITUDE_X & LONGITUDE_X<= b[24]),
     "84" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[24] < LONGITUDE_X & LONGITUDE_X <= b[25]),
     "85" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[25] < LONGITUDE_X & LONGITUDE_X<= b[26]),
     "86" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[26] < LONGITUDE_X & LONGITUDE_X <= b[27]),
     "87" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[27] < LONGITUDE_X & LONGITUDE_X<= b[28]),
     "88" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[28] < LONGITUDE_X & LONGITUDE_X <= b[29]),
     "89" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[29] < LONGITUDE_X & LONGITUDE_X<= b[30]),
     "90" = ( a[3] <= LATITUDE_X & LATITUDE_X <= a[4] & b[30] < LONGITUDE_X & LONGITUDE_X <= b[31]),



     "91" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[1] < LONGITUDE_X & LONGITUDE_X<= b[2]),
     "92" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[2] < LONGITUDE_X & LONGITUDE_X <= b[3]),
     "93" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[3] < LONGITUDE_X & LONGITUDE_X<= b[4]),
     "94" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[4] < LONGITUDE_X & LONGITUDE_X <= b[5]),
     "95" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[5] < LONGITUDE_X & LONGITUDE_X<= b[6]),
     "96" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[6] < LONGITUDE_X & LONGITUDE_X <= b[7]),
     "97" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[7] < LONGITUDE_X & LONGITUDE_X<= b[8]),
     "98" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[8] < LONGITUDE_X & LONGITUDE_X <= b[9]),
     "99" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[9] < LONGITUDE_X & LONGITUDE_X<= b[10]),
     "100" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[10] < LONGITUDE_X & LONGITUDE_X <= b[11]),
      "101" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[11] < LONGITUDE_X & LONGITUDE_X<= b[12]),
     "102" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[12] < LONGITUDE_X & LONGITUDE_X <= b[13]),
     "103" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[13] < LONGITUDE_X & LONGITUDE_X<= b[14]),
     "104" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[14] < LONGITUDE_X & LONGITUDE_X <= b[15]),
     "105" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[15] < LONGITUDE_X & LONGITUDE_X<= b[16]),
     "106" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[16] < LONGITUDE_X & LONGITUDE_X <= b[17]),
     "107" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[17] < LONGITUDE_X & LONGITUDE_X<= b[18]),
     "108" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[18] < LONGITUDE_X & LONGITUDE_X <= b[19]),
     "109" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[19] < LONGITUDE_X & LONGITUDE_X<= b[20]),
     "110" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[20] < LONGITUDE_X & LONGITUDE_X <= b[21]),
      "111" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[21] < LONGITUDE_X & LONGITUDE_X<= b[22]),
     "112" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[22] < LONGITUDE_X & LONGITUDE_X <= b[23]),
     "113" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[23] < LONGITUDE_X & LONGITUDE_X<= b[24]),
     "114" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[24] < LONGITUDE_X & LONGITUDE_X <= b[25]),
     "115" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[25] < LONGITUDE_X & LONGITUDE_X<= b[26]),
     "116" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[26] < LONGITUDE_X & LONGITUDE_X <= b[27]),
     "117" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[27] < LONGITUDE_X & LONGITUDE_X<= b[28]),
     "118" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[28] < LONGITUDE_X & LONGITUDE_X <= b[29]),
     "119" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[29] < LONGITUDE_X & LONGITUDE_X<= b[30]),
     "120" = ( a[4] <= LATITUDE_X & LATITUDE_X <= a[5] & b[30] < LONGITUDE_X & LONGITUDE_X <= b[31]),



     "121" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[1] < LONGITUDE_X & LONGITUDE_X<= b[2]),
     "122" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[2] < LONGITUDE_X & LONGITUDE_X <= b[3]),
     "123" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[3] < LONGITUDE_X & LONGITUDE_X<= b[4]),
     "124" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[4] < LONGITUDE_X & LONGITUDE_X <= b[5]),
     "125" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[5] < LONGITUDE_X & LONGITUDE_X<= b[6]),
     "126" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[6] < LONGITUDE_X & LONGITUDE_X <= b[7]),
     "127" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[7] < LONGITUDE_X & LONGITUDE_X<= b[8]),
     "128" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[8] < LONGITUDE_X & LONGITUDE_X <= b[9]),
     "129" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[9] < LONGITUDE_X & LONGITUDE_X<= b[10]),
     "130" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[10] < LONGITUDE_X & LONGITUDE_X <= b[11]),
     "131" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[11] < LONGITUDE_X & LONGITUDE_X<= b[12]),
     "132" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[12] < LONGITUDE_X & LONGITUDE_X <= b[13]),
     "133" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[13] < LONGITUDE_X & LONGITUDE_X<= b[14]),
     "134" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[14] < LONGITUDE_X & LONGITUDE_X <= b[15]),
     "135" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[15] < LONGITUDE_X & LONGITUDE_X<= b[16]),
     "136" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[16] < LONGITUDE_X & LONGITUDE_X <= b[17]),
     "137" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[17] < LONGITUDE_X & LONGITUDE_X<= b[18]),
     "138" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[18] < LONGITUDE_X & LONGITUDE_X <= b[19]),
     "139" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[19] < LONGITUDE_X & LONGITUDE_X<= b[20]),
     "140" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[20] < LONGITUDE_X & LONGITUDE_X <= b[21]),
     "141" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[21] < LONGITUDE_X & LONGITUDE_X<= b[22]),
     "142" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[22] < LONGITUDE_X & LONGITUDE_X <= b[23]),
     "143" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[23] < LONGITUDE_X & LONGITUDE_X<= b[24]),
     "144" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[24] < LONGITUDE_X & LONGITUDE_X <= b[25]),
     "145" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[25] < LONGITUDE_X & LONGITUDE_X<= b[26]),
     "146" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[26] < LONGITUDE_X & LONGITUDE_X <= b[27]),
     "147" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[27] < LONGITUDE_X & LONGITUDE_X<= b[28]),
     "148" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[28] < LONGITUDE_X & LONGITUDE_X <= b[29]),
     "149" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[29] < LONGITUDE_X & LONGITUDE_X<= b[30]),
     "150" = ( a[5] <= LATITUDE_X & LATITUDE_X <= a[6] & b[30] < LONGITUDE_X & LONGITUDE_X <= b[31]),
.method = "first",
.default = NA
))
```

```{r}
summary(fourtype_995_reg$region)
```
```{r}
fourtype_995_reg_count <-
  fourtype_995_reg %>%
  mutate(hour=
           lubridate::hour(date)) %>%
  mutate(shift = ifelse(hour %in% 6:12, "1",
                                     ifelse(hour %in% 13:20, "2",
                                            ifelse(hour %in% 21:23, "3",
                                                   ifelse(hour %in% 0:5, "3","NA"))))) %>%
  mutate(date_ymd = paste(year, month,day, sep="-" )) %>%
  group_by(date_ymd,shift,region) %>%
  summarise(n())
```

```{r}
fourtype_995_shift_count <-
  fourtype_995_reg %>%
  mutate(hour=
           lubridate::hour(date)) %>%
  mutate(shift = ifelse(hour %in% 6:12, "1",
                                     ifelse(hour %in% 13:20, "2",
                                            ifelse(hour %in% 21:23, "3",
                                                   ifelse(hour %in% 0:5, "3","NA"))))) %>%
  mutate(date_ymd = paste(year, month,day, sep="-" )) %>%
  group_by(date_ymd,shift) %>%
  summarise(n())
```

```{r}
write.csv(fourtype_995_reg_count, file = "fourtype_995_reg_count.csv")
```
